### 2011-01-31 paper/introduction.tex
Many edits...
Added some introduction work

>>>>

Gaits for walking robots are often designed with some explicit or
implicit goal in mind.  For some applications, the design criteria may
be obvious: perhaps the robot needs to move as quickly or as
efficiently as possible, or with minimal power usage or strain on
actuators.  In many cases, however, the objective is more complicated,
requiring simultaneous optimization of several desired traits, each
with its own relative importance.  For example, Honda's Asimo
\cite{_asmio} and Boston Dynamic's Big Dog \cite{_bigdog} both require
gaits that are relatively quick, power efficient, and robust to
changing terrain, but with they vary widely in the importance placed
on each attribute.  A primary concern for Big Dog's gait is that it is
robust to steep terrain, whereas

In other cases, the objective may be more complicated; perhaps it is
desired that the gait be fairly [robust]

\_asimo and \_bigDog very different (and some hexapod?)

Many times gait will be designed and tweaked by hand \cite{_asimo}

here we describe a study, a comparison of few methods. started with
sped, but then not-breaking as well.

When designing gaits for walking robots, often it is desirable that
this gait enable the robot to walk as

Old: design by hand
Newer: Learn gait
  - parmametrized or more free form (HN, ???)
  - in sim or hardware
Us: first time HN in hardware, first time compared to other methods aiming for symmetry on same hardware

Often
these optimizations are done manually by an expert who designs and
tweaks a gait specifically for a given objective.  Other groups have
used learning methods to generate gaits optimized for some metric.
Approaches differ in their starting assumptions, some essentially
tweaking the parameters of a hand-tuned model \cite{chernova}, others
exploring a reasonably compact parameter space \cite{kohl}, and still
others beginning with few assumptions besides periodicity
\cite{zykov}.
